Measuring contrast processing in the visual system using the steady state visually evoked potential (SSVEP)

### 2024-12-03 review.qmd
Added os package

# all package loading and subfunctions defined here
import numpy as np
import matplotlib.pyplot as plt
from matplotlib import colormaps
import scipy as scp
from sklearn.linear_model import LinearRegression

@@

Because SSVEP responses at detection threshold are very small, estimating a threshold is achieved by measuring the contrast response function at relatively high levels (in the linear part of the log-contrast response function prior to saturation), and extrapolating back along the function (either contrast vs response measured at a constant spatial frequency or spatial frequency vs response at a constant contrast level) to estimate its intercept with the x-axis [@Campbell1970] (see @fig-sweepvep). This contrast level has been shown to correspond approximately with psychophysically measured detection thresholds [@campbellVisualEvokedPotential1972; @Norcia1986]. One factor affecting the accuracy of this technique is the presence of noise in the EEG signal which will increase the apparent amplitude of the SSVEP responses across the measurement range. The effect of this noise is particulary apparent for recordings with low SNR or where the slope of the CRF is shallow (and therefore where small changes in the vertical offset of the fit result in large changes in the X-axis intercept). Accurate estimates of thresholds therefore require the experimenter to model this noise and compensate for its effects - as detailed in [@Norcia1989].

>>>>

# all package loading and subfunctions defined here
import os
import numpy as np
import matplotlib.pyplot as plt
from matplotlib import colormaps
import scipy as scp
from sklearn.linear_model import LinearRegression

@@

Because SSVEP responses at detection threshold are very small, estimating a threshold is achieved by measuring the contrast response function at relatively high levels (in the linear part of the log-contrast response function prior to saturation), and extrapolating back along the function (either contrast vs response measured at a constant spatial frequency or spatial frequency vs response at a constant contrast level) to estimate its intercept with the x-axis [@Campbell1970] (see @fig-sweepvep). This contrast level has been shown to correspond approximately with psychophysically measured detection thresholds [@campbellVisualEvokedPotential1972; @Norcia1986]. One factor affecting the accuracy of this technique is the presence of noise in the EEG signal which will increase the apparent amplitude of the SSVEP responses across the measurement range. The effect of this noise is particulary apparent for recordings with low SNR or where the slope of the CRF is shallow (and therefore where small changes in the vertical offset of the fit result in large changes in the X-axis intercept). Accurate estimates of thresholds therefore require the experimenter to model this noise and compensate for its effects, as detailed in @Norcia1989.
